\begin{abstract}
  We study the problem of modular code generation for emulating the
  electrical conduction system of the heart, which is essential for the
  validation of implantable devices such as pacemakers. In order to
  develop high fidelity models, it is essential to consider the
  operation of hundreds, if not millions of conduction elements, called
  \emph{nodes} of the heart. Published results so far, however, have
  considered a maximum of 33~nodes, modelled as \acf{HIOA}. The
  behaviour of this model is captured using the well known commercial
  tool \simulink. These approaches are limiting due to the lack of
  model fidelity %as well as the lack of modelling the re-entrant nature
  of the conduction system.

  In this paper, 
  %we have developed a radically new approach to tackle
  %the aforementioned drawbacks.
  we first develop a semantic preserving
  modular compilation approach for a network of \ac{HIOA}, by proposing
  to translate them to a network of \acp{FSM}. We then demonstrate that
  a delayed synchronous composition of the cardiac nodes enables modular
  code generation that is both semantic preserving and efficient. In
  addition to the above example, we have developed several examples from
  other domains to compare \simulink and the developed tool called
  \textit{Piha}. The results show that we are able to generate code which, for 
  the cardiac model, is 60\% smaller in binary size while executing 20~times
  faster when compared to \simulink.  We have also compared the
  scalability of the proposed approach relative to \simulink to prove
  its relative superiority.

  \ignore{Real-time emulation of a plant is often desirable to
    facilitate the testing of controllers under realistic conditions.
    Plants which exhibit continuous dynamics can be well modelled
    through the use of \acf{HIOA}, and so code generation from \ac{HIOA}
    that is suitable for real-time emulation is desirable.  In the case
    of plants which are modelled by a network of \acp{HIOA}, such code
    generation must be able to emulate the entire overall system through
    parallel composition.

    In this paper, we propose a new tool (named \ourTool) for the
    modular code generation from \ac{HIOA} that is amenable to use in
    both the real-time emulation or simulation of plants.  We illustrate
    the suitability of this approach through the running example of a
    human heart, where real-time emulation is desired for the
    verification of cardiac pacemakers.  We compare the proposed
    approach to \simulink, a tool commonly used in the modelling of
    plants, to show that we are able to generate code that is on average
    54\% smaller while executing 9.8 times faster.  We finish by showing
    the scalability of our approach in order to illustrate its potential
    in allowing real-time emulation of complex \ac{HIOA} networks.}
\end{abstract}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../DATE2016_codegen"
%%% End:
