\section{Introduction}

Numerous cases of death and injuries due to malfunction of 
cyber-physical devices such as  pacemakers have been reported.
In 1990-2000, close to 200,000 pacemakers have been recalled
due to software related failures~\cite{alemzadeh13}.
 One reason that these malfunctions
arise is due to the lack of proper validation.
Unlike the ideas of hardware-in-the-loop testing [ref],
it is not possible to test on actual heart.
Further, unlike the hardware that is almost identical 
during mass production, each individual heart is different.
Thus there is a need to develop a virtual heart that is tailored
to an individual person and achieves
 personalised healthcare~\cite{Trayanova2014}. This idea can be extended 
to a network of human organs, resulting in a virtual human.

Typically these biological  models are  developed by biomedical engineers.
They mimic the heart's working at the
molecular level~\cite{Trayanova2014}. 
To simulate one heart beat takes severely hours, if not days~[].
These models are very computationally intensive and 
are not for real-time emulation,
which is required for closed-loop testing of time-critical 
controllers such as cardiac pacemakers.
Further, the models are 
 very precise resulting in sophisticated models that are not amenable for  
formal verification. 
Thus, there is a need to develop abstract models by computer systems engineers that  
(1)  \emph{capture the behaviour} of the heart (plant) from a pacemaker (controller) point of view,
(2) \emph{real-time emulation} of the heart such that it is possible for closed-loop simulation and
allows for (3) \emph{formal verification} of functional and timing properties.

